|

### 2023-02-06 paper.Rmd
Mon Feb  6 19:00:07 CET 2023: update-remote.sh

@@

The first interesting observation from this experiment is, that the pre-trained DAE-GP shows slightly lower mean RMSE (higher fitness) but a higher median RMSE (lower fitness) than regular DAE-GP for both the training and the testing set in overall fitness. Regarding the presence of overfitting, both DAE-GP variants show only a very small gap between the testing and training fitness which indicates a good generalization behavior. Another interesting observation from figure \@ref(fig:airfoil-median-fitness-30gens) is that pre-trained DAE-GP is faster at improving fitness than regular DAE-GP, this is especially true if only looking at the first 10 generations

@@

Figure \@ref(fig:symReg-LevDiv) shows the median levenshtein edit distance as a metric for population diversity over the evolutionary search.

>>>>

REG_TRAIN_MED_10F <- py$D_AIRFOIL_2hl$REG_TRAIN_MED_10F
REG_TEST_MED_10F <- py$D_AIRFOIL_2hl$REG_TEST_MED_10F
PT_TRAIN_MED_10F <- py$D_AIRFOIL_2hl$PT_TRAIN_MED_10F
PT_TEST_MED_10F <- py$D_AIRFOIL_2hl$PT_TEST_MED_10F
GP_TRAIN_MED_10F <- py$D_AIRFOIL_2hl$GP_TRAIN_MED_10F
GP_TEST_MED_10F <- py$D_AIRFOIL_2hl$GP_TEST_MED_10F

@@

The first interesting observation from this experiment is, that the pre-trained DAE-GP shows slightly lower mean RMSE (higher fitness) but a higher median RMSE (lower fitness) than regular DAE-GP for both the training and the testing set in overall fitness. Regarding the presence of overfitting, both DAE-GP variants show only a very small gap between the testing and training fitness which indicates a good generalization behavior. Another interesting observation from figure \@ref(fig:airfoil-median-fitness-30gens) is that pre-trained DAE-GP is faster at improving fitness than regular DAE-GP, this is especially true if only looking at the first 10 generations. The median best RMSE on the test set after 10 generations for pre-trained DAE-GP is `r round(PT_TEST_MED_10F, 3)` which is smaller by a factor of `r round( PT_TEST_MED_10F / REG_TEST_MED_10F, 3)` than regular DAE-GP with a median best RMSE of `r round( REG_TEST_MED_10F, 3)`

@@

Figure \@ref(fig:symReg-LevDiv) shows the median levenshtein edit distance as a metric for population diversity over the evolutionary search. It clearly shows that pre-training does increase the population diversity for DAE-GP consistently for all tested benchmark problems.

### 2023-02-06 paper.tex
Mon Feb  6 19:00:07 CET 2023: update-remote.sh

The first interesting observation from this experiment is, that the pre-trained DAE-GP shows slightly lower mean RMSE (higher fitness) but a higher median RMSE (lower fitness) than regular DAE-GP for both the training and the testing set in overall fitness. Regarding the presence of overfitting, both DAE-GP variants show only a very small gap between the testing and training fitness which indicates a good generalization behavior.

>>>>

The first interesting observation from this experiment is, that the pre-trained DAE-GP shows slightly lower mean RMSE (higher fitness) but a higher median RMSE (lower fitness) than regular DAE-GP for both the training and the testing set in overall fitness. Regarding the presence of overfitting, both DAE-GP variants show only a very small gap between the testing and training fitness which indicates a good generalization behavior. Another interesting observation from figure \ref{fig:airfoil-median-fitness-30gens} is that pre-trained DAE-GP is faster at improving fitness than regular DAE-GP, this is especially true if only looking at the first 10 generations. The median best RMSE on the test set after 10 generations for pre-trained DAE-GP is 17.093 which is smaller by a factor of 0.558 than regular DAE-GP with a median best RMSE of 30.658
